A Simplified Spectral Deferred Correction Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium

### 2020-10-23 simplified_sdc_intro/paper.tex
add a figure
more tables

@@

The domain has a size $[0, L]^2$, and the timestep is fixed as:
\begin{equation}
\Delta t = 5\times 10^{-4} \left ( \frac{128}{N} \right )~\mathrm{s}
\end{equation}
where $N$ is the number of zones in each direction.

@@

>>>>

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_strang} Convergence ($L_1$ norm) for the reacting convergence problem using SDC integration.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.795 \times 10^{18}$  & 2.044  & $6.777 \times 10^{17}$  & 2.554  & $1.154 \times 10^{17}$  \\
 $\rho u$                    & $6.798 \times 10^{26}$  & 2.449  & $1.245 \times 10^{26}$  & 2.889  & $1.680 \times 10^{25}$  \\
 $\rho v$                    & $6.798 \times 10^{26}$  & 2.449  & $1.245 \times 10^{26}$  & 2.889  & $1.680 \times 10^{25}$  \\
 $\rho E$                    & $2.452 \times 10^{35}$  & 2.352  & $4.804 \times 10^{34}$  & 2.742  & $7.179 \times 10^{33}$  \\
 $\rho e$                    & $2.262 \times 10^{35}$  & 2.321  & $4.527 \times 10^{34}$  & 2.822  & $6.404 \times 10^{33}$  \\
 $T$                         & $2.236 \times 10^{21}$  & 1.691  & $6.927 \times 10^{20}$  & 2.481  & $1.240 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.879 \times 10^{18}$  & 2.020  & $7.096 \times 10^{17}$  & 2.529  & $1.229 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.697 \times 10^{17}$  & 1.950  & $4.393 \times 10^{16}$  & 2.231  & $9.357 \times 10^{15}$  \\
 $\rho X(\isotm{O}{16})$     & $1.686 \times 10^{14}$  & 1.659  & $5.338 \times 10^{13}$  & 1.957  & $1.375 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.795 \times 10^{8}$   & 2.044  & $6.777 \times 10^{7}$   & 2.554  & $1.154 \times 10^{7}$   \\
\enddata
\end{deluxetable}

@@

The domain has a size $[0, L]^2$, and the timestep is fixed as:
\begin{equation}
\Delta t = 10^{-3} \left ( \frac{64}{N} \right )~\mathrm{s}
\end{equation}
where $N$ is the number of zones in each direction.

@@

Figure~\ref{fig:nse_ye} shows the $Y_e$ profile for the Strang evolution case.

\begin{figure}[t]
\centering
\plotone{ye_plot}
\caption{\label{fig:nse_ye} Profile of $Y_e$ through the middle of the domain (slicing along $x$)
for the $128^2$ Strang method II NSE test simulation.}
\end{figure}
